Stage-Splitting a Modal Language

### 2014-06-22 paper/splitting.tex
Started adding some arguments regarding splitting.

>>>>

Motivate splitting here.  (Depends on intro)
Consider splitting at \bbtwo. 
The basic idea is that, for a given input program, we want to find all of the stage \bbone\ content, pull that out into a single term, 
and also produce a stage \bbtwo\ term, which takes the results of the stage \bbone\ part and produces the final answer.
We call these two parts the {\em precomputation} and the {\em residual}, respectively.
More formally, we want to take some $\coltwo e A$ and produce a $p : \tau$ and a $r : \tau \to A$ such that $e$ and $(r~p)$ reduce to the same value.
Consider the following stage \bbtwo\ example:
\begin{lstlisting}
if 6*7 > 41 then
	hold{1+2} * 3
else 
	hold{2*3} + hold {4*5}
\end{lstlisting}
Under the definitions above, this should split into:
\begin{lstlisting}
(1+2,2*3,4*5)
\end{lstlisting}
and
\begin{lstlisting}
fn (l1,l2,l3) => 
    if 6*7 > 41 then l1 * 3 else l2 + l3
\end{lstlisting}
Essentially what we've done is find all of the $\pause$ expressions, 
bundle them into a tuple in then precomputation, 
and then unbundle them into the correct place in the residual.
Note how splitting has the same speculative behavior as our \lang\ dynamics,
wherein we run the stage \bbone\ code in {\em both} branches of the stage \bbtwo\ {\tt if} expression.

Now consider splitting the following expression, where the {\tt if} is at stage \bbone, rather than stage \bbtwo:
\begin{lstlisting}
prev {
  if 6*7 > 41 then
    next{1+hold{2*3}}
  else 
    next{4+5}
}
\end{lstlisting}
This splits into
\begin{lstlisting}
if 6*7 > 41 then inL (2*3) else inR ()
\end{lstlisting}
and
\begin{lstlisting}
fn l => 
  case l of
    l1 => 1+l1
  | () => 4+5
\end{lstlisting}
In this example, we

[develope the more formal version...]

  $\diatwo [\cdot;\cdot] e q$ and $\reduce q v$ iff $\reduce {r~p} {v}$.

\input{figures/splitting-term}
\input{figures/splitting-sumfun}
